\documentclass[]{deedy-resume-reversed}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}

\begin{document}

\namesection{Varshini}{Suresh}{
\href{mailto:varshisuresh25@gmail.com}{varshisuresh25@gmail.com}
|
+91 94430 41745
|
Chennai, Tamil Nadu
|
\href{https://www.linkedin.com/in/varshini-suresh-r/}{LinkedIn}
|
\href{https://github.com/varshinis25}{GitHub}
}

\begin{minipage}[t]{0.65\textwidth}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SUMMARY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{ROLE HIGHLIGHTS}

Data Analytics professional with experience in Procurement Operations, Business Intelligence, Machine Learning, and Data Visualization. Skilled in Python, SQL, Power BI, Excel, and Predictive Analytics for transforming operational and procurement data into actionable business insights. Experienced in vendor evaluation, spend analysis, inventory monitoring, KPI reporting, and dashboard development to support data-driven decision-making and process optimization.

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Bigzel Technologies}
\descript{| Data Science Intern}
\location{Jan 2026 – Present | Hybrid | Chennai}
.
\begin{tightemize}
\item Cleaned and analyzed datasets using Python, SQL, Pandas, and NumPy to support data-driven insights and predictive analytics.
\item Developed Power BI dashboards and KPI reports to monitor business performance, enabling stakeholders to track key operational metrics effectively.
\item Applied statistical analysis and machine learning techniques to identify trends, anomalies, and predictive patterns supporting business insights.
\end{tightemize}

\sectionsep

\runsubsection{ES HOSPITAL}
\descript{| Biomedical Engineering Intern}
\location{May 2023 – Jul 2023}

\begin{tightemize}
\item Assisted vendor evaluation, quotation analysis, and procurement documentation processes to support cost-effective purchasing decisions.
\item Analyzed inventory utilization and maintenance expenditure data using Excel to support procurement planning and resource allocation.
\item Collaborated with procurement, engineering, and clinical teams to improve equipment availability and support operational efficiency.

\end{tightemize}

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{Autism Spectrum Disorder Prediction using Machine Learning}
\descript{\textbf{| Tech Stack:} Python | Pandas | Scikit-Learn | SVM | SelectKBest}

\begin{tightemize}
\item Analyzed 700+ clinical assessment records and performed preprocessing, feature engineering, and feature selection to improve model performance.
\item Developed and optimized a Support Vector Machine (SVM) classification model achieving 89 percent prediction accuracy.
\item Evaluated model effectiveness using accuracy, precision, recall, and confusion matrix metrics.

\end{tightemize}

\sectionsep

\runsubsection{Employee Attrition Analysis and Prediction}
\descript{\textbf{| Tech Stack:} Python | SQL | Power BI | Machine Learning}

\begin{tightemize}
\item Conducted exploratory data analysis to identify key factors influencing employee attrition and workforce retention.
\item Built predictive models to classify attrition risk and support proactive HR decision-making.
\item Designed Power BI dashboards visualizing workforce KPIs, attrition trends, and retention insights.
\end{tightemize}

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}

Github://
\href{https://github.com/varshinis25}{https://github.com/varshinis25}

LinkedIn://
\href{https://www.linkedin.com/in/varshini-suresh-r/}{https://www.linkedin.com/in/varshini-suresh-r/}

\end{minipage}
\hfill
\begin{minipage}[t]{0.30\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{Bharathidasan University}

\descript{Master of Business Administration} | {Finance Management | (Expected 2027)}



\subsection{Anna University} | {\textbf{Chennai Institute of Technology}}

\descript{Bachelor of Engineering} | {Biomedical Engineering | CGPA: 8.5/10}

\location{Chennai}

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}

\subsection{Programming}

\textbullet{} Python \textbullet{} SQL \textbullet{} Java


\sectionsep

\subsection{Analytics}

\textbullet{} Data Analysis \textbullet{} Exploratory Data Analysis (EDA) \textbullet{} Data Cleaning \textbullet{} Feature Engineering \textbullet{}Statistical Analysis \textbullet{} Predictive Analytics \textbullet{} Machine Learning

\sectionsep

\subsection{Visualization}

\textbullet{} Power BI \textbullet{} Excel \textbullet{} Tableau

\sectionsep

\subsection{Libraries}

\textbullet{} Pandas \textbullet{} NumPy \textbullet{} Scikit-Learn 
\textbullet{} Matplotlib

\sectionsep

\subsection{Procurement}

\textbullet{} Direct Procurement \textbullet{} Vendor Evaluation \textbullet{} Inventory Monitoring  \textbullet{} Spend Analysis \textbullet{} KPI Reporting


\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TOOLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Tools}

\textbullet{} MySQL \textbullet{} Git \textbullet{} GitHub \textbullet{} Jupyter Notebook
\textbullet{} UIPath

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ERP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{ERP}

\textbullet{} SAP Ariba \textbullet{} SAP
(EHP-7[MM module])

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ACHIEVEMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{KEY ACHIEVEMENTS}

\textbullet{} Achieved 89 percent accuracy in a healthcare machine learning prediction model.

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CERTIFICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certifications}

\textbullet{} \textbf{Certificate in Data Science and AI} | Course-Inn Academy, Chennai

\textbullet{} \textbf{Cisco Python Essentials}

\textbullet{} \textbf{Database Management Systems (DBMS)}

\textbullet{} \textbf{UIPath Robotic Process Automation}

\sectionsep


\end{minipage}

\end{document}
